%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Engineer 2} % Job title
    {Microsoft Vancouver - OS Fundamentals} % Organization
    {Vancouver, BC, Canada} % Location
    {Since March 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
	      \item {Leading a team developing Microsoft's Operating System.}
        \\
     	\technologies{C, C++, C\#}
      \end{cvitems}
    }


%---------------------------------------------------------
  \cventry
    {Software Engineer 2} % Job title
    {Microsoft Vancouver - BigPark} % Organization
    {Vancouver, BC, Canada} % Location
    {Dec. 2018 - Mar. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
	      \item {De-deprecated Microsoft Paint by implementing several new accessibility features and addressing software compliance items.}
	      \item {Addressed numerous security and accessibility issues within Microsoft's 3D ecosystem, including Paint3D and 3D Viewer.}
	      \item {Improved Microsoft Photos resulting in 50\% reduction of service load to OneDrive and 10\% improvement in app stability.}
        \\
     	\technologies{C, C++, C\#, Python, TypeScript, MFC, OLE/COM, Microsoft Active Accessibility, HyperV, Win32, UWP}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Microsoft Vancouver - Storefronts Team} % Organization
    {Vancouver, BC, Canada} % Location
    {Oct. 2017 - Nov. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
	      \item {Redesigned and implemented a Point-of-Sale System using a micro-service architecture with excellent robustness and scalability characteristics.}
	      \item {Maintained the software that powers the Microsoft retail stores and responded to critical service-impacting events.}
	      \item {Developed tools and frameworks to aid rapid application development and enhance consumer experience in retail stores.}
        \\
     	\technologies{C\#, Python, TypeScript, UWP, SQL, CosmosDB, Azure ServiceFabric, UI Automation, ASP.NET}
      \end{cvitems}
    }

\iffalse
  % Entry ommitted from resume due to length of time
%---------------------------------------------------------
  \cventry
    {Software Engineering Co-Op} % Job title
    {Microsoft Studios ``The Coalition''} % Organization
    {Vancouver, BC, Canada} % Location
    {Jan. 2016 - Aug. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Created a custom, proprietary system for patching game content after release.}
        \item {Worked with senior engineers in resolving crashes and performing low-level optimizations.}
        \item {Developed tools to improve iteration and enable automatic analysis and verification.}
        \\
     	\technologies{C++, C\#, Python, AMD64 Assembly, Unreal Engine 4, Visual Studio, Microsoft XDK, Perforce.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Gameplay Programmer} % Job title
    {Behaviour Interactive} % Organization
    {Montréal, QC, Canada} % Location
    {Sep. 2014 - Dec. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed and improved features in gameplay, networking and graphics rendering.}
        \item {Worked closely with game designers on implementing new mechanics and customizations.}
        \item {Assisted in performing memory and processing optimizations to the game.}
        \\
        \technologies {C\#, CG, Unity, Unreal Engine 4, Visual Studio, Python, Nvidia Nsight.}
      \end{cvitems}
    }
\fi

\end{cventries}
