%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Extracurricular Activity}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

% This section sums up all extracurriculars + volunteering, ordered by most recent

%---------------------------------------------------------
  \cventry
    {VP Competitions} % Affiliation/role
    {Concordia Software Eng. and Comp. Sci. Society} % Organization/group
    {Montréal, QC, Canada} % Location
    {Since May 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Organized events, tryouts and practice sessions for students interested in competitive programming.}
        \item {Led teams of students and alumni representing Concordia University in IEEE Xtreme 10.0 and the Computer Science Games 2017.}
        \item {Began creating a stronger competitive programming community, centered around regular training and participation.}
      \end{cvitems}
    }
    \vspace{2.0mm}
%---------------------------------------------------------
  \cventry
    {Teaching Assistant} % Affiliation/role
    {Kids Code Jeunesse} % Organization/group
    {Montréal \& Vancouver, Canada} % Location
    {Since May 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Helped children learn programming through making games by guiding them through a series of well-defined tasks.}
        \\
        \technologies{MIT Scratch.}
      \end{cvitems}
    }
    \vspace{2.0mm}

%---------------------------------------------------------
  \cventry
    {VP Internal Affairs} % Affiliation/role
    {Concordia Software Eng. and Comp. Sci. Society} % Organization/group
    {Montréal, QC, Canada} % Location
    {May 2014 to Jan. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Helped maintaining the Society’s infrastructure, including servers, office space and internal documents.}
        \item {Assisted fellow executives of the society in performing their responsibilities.}
        \item {Promoted the practice of programming to other engineering disciplines.}
      \end{cvitems}
    }
    \vspace{2.0mm}

%---------------------------------------------------------
  \cventry
    {IT Support Volunteer} % Affiliation/role
    {FEM International} % Organization/group
    {Montréal, QC, Canada} % Location
    {Jan. 2013 to Apr. 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Migrated all office computers to Ubuntu Linux , reconfigured for ease of use in their workplace.}
        \item {Diagnosed and solved issues affecting faulty computer hardware, providing on-site support.}
        \item {Drafted simplified documentation for troubleshooting and self-sustainment of the system.}
      \end{cvitems}
    }
    \vspace{2.0mm}

%---------------------------------------------------------
  \cventry
    {Catholic Missionary} % Affiliation/role
    {Our Lady of Guadalupe Parrish} % Organization/group
    {Caracas, Venezuela} % Location
    {Apr. 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Stayed in a community 200 kilometers from the Colombian-Venezuelan border for a week.}
        \item {Organized day-long activities to work with local children and teenagers.}
        \item {Coordinated with other missionary members to address issues within the community (violence, drugs).}
      \end{cvitems}
    }
    \vspace{2.0mm}
    
%---------------------------------------------------------

\end{cventries}
