%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Personal Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \vspace{1.5mm} % Additional compesation due to weird formatting
  \cventry
    {Kinetic Intelligent Tracking System (KITS)} % Project Title
    {} % Organization/group
    {} % Location
    {Sep. 2016 - Jul. 2017} % Date
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Created a system to detect the risk of ACL injury in athletes using the Microsoft Kinect v2.}
        \item {Drafted the high-level system design and led teammates through planning and execution.}
        \item {Contributed in implementing major system components, including an ORM system and an OpenGL graphics backend.}
        \\
        \technologies{C++, Qt, OpenGL, Crypto++, RapidJSON, SQLite, Android, Kinect SDK.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Concordia Engineering Games Machine Team 2017} % Project Title
    {} % Organization/group
    {} % Location
    {Sep. 2016 - Jan. 2017} % Date
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Assisted in creating a semi-autonomous robot with an inter-disciplinary engineering team.}
        \item {Led the software sub-team from design to delivery, including complete integration with electrical and mechanical designs.}
        \item {Created system-critical software modules, including desktop control client, hardware drivers and code "hot-reload" logic.}
        \\
        \technologies{Java, Linux, Raspberry Pi, I2C, PWM, Python, Swing toolkit.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {DotHike Android App} % Project Title
    {} % Organization/group
    {} % Location
    {Sep. 2015 - Dec. 2015} % Date
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Along with three classmates, made an Android application that makes use of wearable devices}
        \item {Created the application backend architecture, designed for extensibility and addition of new devices.}
        \item {Drafted and developed rigorous test for all Hardware and Software components.}
        \\
        \technologies{Android SDK, SQLite3, Bluetooth LE, Google Maps API, Python, Java, Git.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Pokedex App} % Project Title
    {} % Organization/group
    {} % Location
    {Feb. 2015 - Dec. 2015} % Date
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Created an application to manage collections and review game progress, to practice standardized software practices.}
        \item {Led the design of features, distribution of tasks and the peer code review of major additions.}
        \item {Designed a robust software architecture to model and store data and assets.}
        \\
        \technologies{Android SDK, SQLite3, REST API, Python, Java, Git.}
      \end{cvitems}
    } 

%---------------------------------------------------------
  \cventry
    {Wizards of RGB} % Project Title
    {} % Organization/group
    {} % Location
    {Jan. 2014 - Jul. 2015} % Date
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Worked in a four person team to develop a videogame in less than 48 hours.}
        \item {Collaborated in developing object classes and in-game events through the Unity API using C\#.}
        \item {Performed maintenance and restructuring to publish the application through the Google Play Store.}
        \\
        \technologies{C\#, Unity, Visual Studio, Audacity.}
      \end{cvitems}
    } 

%---------------------------------------------------------
\end{cventries}
